---
title: "Student Sit In"
author: "Jose Guzman"
date: "10/26/2019"
output: 
  html_document:
    toc: true
    number_sectons: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ONE SHOT assignment!
this is an extra credit assignment, must be completed Monday Oct 28, turn-in closes at midnight!

## Problem statement: 
Students at UCD- is there a relation between where one sits and one's major? 

## Introduction  

<!-- where is the data found?  Is this an experiment or an observational study?  !-->

Data from this study came from a study of 173 students at UC David.



```{r include=FALSE, echo=FALSE}
library(tigerstats)
data(ucdavis1)

```

$H_0$: there is no relationship between one's major and where one sits in a class   
$H_A$: where one sits in class and one's major are related  

<!-- Get the data: !-->

names of the data in the data frame

```{r echo=FALSE}
UCDdataframe = data.frame(seat=ucdavis1$Seat, major=ucdavis1$class, data=ucdavis1)
names(UCDdataframe)
```
## Methods
Both variables in this are categorical. We will us a bar chart to show the graphical data, a cross table to show the numerical summary, and a Chi- Squared test to show the inferential results. 

<!--  describe analysis methods here 
what are the variable types, and indicate gaphical, numerical, and inferential methods appropriate
for this question  !--> 


## Data summary

**Graphical summary**
put the graphic description of the data here

```{r}
barchartGC(~ seat+major,data=UCDdataframe)
```


The graph is showing that a majority of the non liberal arts students prefer to be seated in the middle. The more of the liberal arts students prefer to be seated in the middle than the front and back.  


**Numerical summary**
put numerical summary here

```{r}
tab=xtabs(~seat+major,data=UCDdataframe)
print(tab)
```

The numberical table suggests that liberal arts students prefer to sit in the middle and non liberal arts students prefer to sit in the middle. 

## Inferential Results
put the inferential test for the the null hypothesis here

```{r}
chisqtestGC(tab)
```

the P-Value is 0.2173

## Results and conclusions

Since the P-Value is greater than .05, we reject the null hypothesis and conclude that there is not enough information to say that there is a relationship between the major of a student and where they prefer to sit. 

<!-- explain-- is there evidence that certain majors tend to sit in particular areas of the class?  Can the results of this test be generalized to all majors in all universities? !---



<!--
push results to your github account, turn in the URL

--OR--

If you did not fork my repo to your github account,
create a repository in your github account for this project, get the URL for that repo and 
(in the terminal window..)

$git remote add origin URL_of_your_github_repo
$git push -u origin master

!-->